---
title: "Attendance and Quizes / Katılım ve Quizler"
date: "20240722"
format: html
typora-copy-images-to: images
---

# Derse Katılım / Attendance

Zoom üzerinden süre olarak katılımınız alınarak, toplam ders süremize[^1] göre oran hesaplanmıştır. Dersin üçte birinden (1/3 ya da 0.3) az katılan öğrenci o derse katılmamış sayılacaktır.

Aşağıdaki tablolarda her bir ders günü için Zoom süresi ve katılım oranı verilmiştir. (**ŞU ANDA SADECE 19 TEMMUZ GÜNÜ YAPILAN DERSE GÖRE HESAPLAMA YAPILMIŞTIR**)

::: {.callout-caution collapse="true" icon=false}
## Click for translation
Your participation time has been recorded via Zoom, and a ratio has been calculated based on our total lesson duration. A student who participates less than one-third (1/3 or 0.3) of the lesson will be considered as not having attended that lesson.

In the tables below, the Zoom duration and participation ratio for each lesson day are provided. (**THE DATA BELOW ONLY CONSIDERS JULY 19TH LECTURE**)
:::

## Group1 / Grup1 Türkçe

```{r}
#| echo: false
#| warning: false
#| messages: false
library(tidyverse)
library(DT)
library(glue)
read_csv("attandance_20240719_tr.csv") |>
  arrange(student_id) |>
  datatable(rownames = FALSE)
```

## Group2 / Grup2 İngilizce

```{r}
#| echo: false
#| warning: false
#| messages: false
read_csv("attandance_20240719_en.csv") |>
  arrange(student_id) |>
  datatable(rownames = FALSE)
```

# Quizler

Derste yapılan quizlerde en az bir doğru cevap verilmesi gerekmektedir. Bütün cevapları yanlış olan öğrenciler quize girmemiş sayılacaktır.

Aşağıdaki tablolarda her bir quiz için doğru cevap ve toplam soru sayısı verilmiştir.

::: {.callout-caution collapse="true" icon=false}
## Click for translation
In the quizzes given during the lesson, at least one correct answer is required. Students who have all answers incorrect will be considered as not having taken the quiz.

In the tables below, the number of correct answers and total number of questions for each quiz are provided.
:::

## Group1 / Grup1 Türkçe

```{r}
#| echo: false
#| warning: false
#| messages: false
data <- readxl::read_excel("quiz1_20240719_tr.xlsx","Participant Data")

data |>
      janitor::clean_names() |>
      select(first_name, correct, 8:12) |>
      mutate(total = 3) |>
      mutate( new_column = glue("{correct} / {total}")) |>
      select(student_id=first_name, result=new_column) |>
      arrange(student_id) |> 
      datatable(rownames=FALSE)
```

## Group2 / Grup2 İngilizce

```{r}
#| echo: false
#| warning: false
#| messages: false
data <- readxl::read_excel("quiz1_20240719_en.xlsx","Participant Data")

data |>
  janitor::clean_names() |>
  select(first_name, correct, 8:12) |>
  rowwise() |>
  mutate(total = sum(across(2:7))) |>
  ungroup() |>
  mutate(total = max(total), new_column = glue("{correct} / {total}")) |>
  select(student_id=first_name, result=new_column) |>
  arrange(student_id) |>
  datatable(rownames=FALSE)
```


[^1]: Beklenen ders süresi (yaklaşık 3 saat) değil, işlenen süre. Yani maksimum süre, ders süresi olarak alınmıştır.
