---
title: "Midterm Results / Vize Sonuçları"
date: "20240721"
format: html
typora-copy-images-to: images
---


## Grup 1 (Türkçe) sonuçları

```{r}
#| echo: false
#| warning: false
#| messages: false
library(tidyverse)
library(DT)
tr_data <- read_csv("tr-midterm-scores.csv",col_types = "ci")
en_data <- read_csv("en-midterm-scores.csv",col_types = "ci")
```

Sınava katılan öğrenci sayısı: **`r nrow(tr_data)`** ve vize notlarının ortalaması: **`r round(mean(tr_data$midterm),1)`**. Aşağıda, vize notlarının dağılımı verilmiştir.

```{r}
#| echo: false
#| fig-height: 4
tr_data |>
  select(id, midterm) |>
  count(midterm) |>
  ggplot(aes(x=midterm, y=n)) +
  geom_col() +
  scale_x_continuous(breaks = seq(5, 100, by = 5)) +
  labs(x = "Vize Notu", y = "Öğrenci Sayısı") +
  theme_linedraw()
```
Aşağıdaki tabloda, sayfaları gezinerek veya arama kutusunda öğrenci numaranızı arayarak notlarınızı öğrenebilirsiniz.



```{r}
#| echo: false

tr_data |> datatable(rownames = FALSE)
```

## Group 2 (EN) results

Total number of students took the exam: **`r nrow(en_data)`** and average score is: **`r mean(en_data$midterm)`**. Below is the distribution of scores:

```{r}
#| echo: false
#| fig-height: 4
en_data |>
  select(id, midterm) |> 
  count(midterm) |> 
  ggplot(aes(x=midterm, y=n)) + 
  geom_col() + 
  scale_x_continuous(breaks = seq(5, 100, by = 5)) +  
  labs(x = "Midterm Score", y = "Number of Students") + 
  theme_linedraw() 
```

And here's the scores. You can scroll pages or search for your student number in search box.


```{r}
#| echo: false

en_data |> datatable(rownames = FALSE)
```

