---
title: "Linear Regression with R"
format: html
typora-copy-images-to: images
---

## A Polynomial Model 

Here we have a data `mtcars {datasets}` that was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models). We will find a mathematical model between `Weight (wt)` and `Displacement (disp)` parameters. So let's find the most suitable model. Please draw the plot, determine the degree of equation (first, second of third) and draw the curve.  


```{r}
mtcars
```


```{r}
plot(mtcars)
```


```{r}
plot(mtcars$disp, mtcars$wt)
```

```{r}
first_wd <- lm(wt ~ disp, data=mtcars)
summary(first_wd)
```

```{r}
second_wd <- lm(wt ~ disp + I(disp^2), data=mtcars)
summary(second_wd)
```

```{r}
third_wd <- lm(wt ~ disp + I(disp^2) + I(disp^3), data = mtcars)
summary(third_wd)
```

```{r}
plot(mtcars$disp,mtcars$wt)
curve(2.243e-07*x^3 -1.807e-04*x^2 +4.945e-02*x -1.111e+00,add=TRUE)
```


```{r}
best_model <- lm(wt ~ poly(disp,15), data=mtcars)
summary(best_model)
```

```{r}
pred <- predict(best_model, data.frame(disp=50:500))
plot(mtcars$disp, mtcars$wt)
points(50:500, pred, type="l")

```

```{r}
predict(third_wd, data.frame(disp=420))
```


```{r}
predict(best_model, data.frame(disp=420))
```

```{r}
predict(best_model, data.frame(disp=c(20,420, 500)))
```

> So, the "best" model is **not** best at all..

## Train/Test split

Let's understand the topic of [overfitting](https://www.investopedia.com/terms/o/overfitting.asp).

Split the data into train and test. Train the model with "training" data. Then predict with "test" data. 

```{r}
sample(1:32, 5, replace=FALSE)
```


```{r}
set.seed(2)
idx <- sample(1:32, 5, replace=FALSE)
idx
```

```{r}
test <- mtcars[idx,]

test
```

```{r}
train <- mtcars[-idx,]
train
```

```{r}
third_deg <- lm(wt ~ poly(disp,3), data = train)
summary(third_deg)$r.squared
```


```{r}
predict(third_deg, test)
```

```{r}
test$third_pred <- predict(third_deg, test)
test
```

```{r}
fifteen_deg <- lm(wt ~ poly(disp,15), data=train)
summary(fifteen_deg)$r.squared
```

```{r}
predict(fifteen_deg, test)
```

```{r}
test$fifteen <- predict(fifteen_deg, test)

test[c("disp","wt","third_pred","fifteen")]
```

As you can see, "fifteenth degree" model memorized (i.e overfitted) the data and predicts horribly.
